---
title: "Higher Correlations Finder"
author: "Rodrigo Quintana"
date: "2017-11-28"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Description

HCF, as your name states, is a tool for finding the variable that best correlates with a response variable of interest in a given dataset

## What does it do?

- Gives you the name of the variable with higher correlation with your response variable, its correlation index, tells you if it´s positive or negative and plots both variables to give you a visual hint on the nature of that correlation

```{r pressure}
plot(mtcars$disp,mtcars$mpg)

```





## What problem does it solve?

- It gives you a quick summary on what variable happens to relate the most to a response variable. This can be used to choose a predictor in a simple predictive model and to get insight on the potential explanations for the variable of interest, if the goal is more descriptive

## Conclusion

This is a very simple and easy to use app for getting quick insight on a dataset. You'll came out of it with a nice and concise synthesis of the higher correlated variable and with a cool visualization for a very first exploratory approach



